Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2023-12-28 Manuscript Analyses/manuscript_analysis.Rmd
Small edits to des stats code

# Calculating pretest and posttest intelligibility for the listeners
pl_int <- data %>%
  dplyr::group_by(id, speaker, type) %>%
  dplyr::mutate(pwc = (sum(correct_words)/sum(target_number))*100,
                best_win = ifelse(win_r < win_l, win_r, win_l)) %>%
  dplyr::summarize(mean_pwc = mean(pwc, na.rm = T),
                   across(c(contains("_c"), contains("_u"), contains("win")),
                          ~first(.x)
                          )) %>%
  dplyr::ungroup()

@@

pl_int <- pl_int %>%
  dplyr::mutate(type = as.factor(type),
                type = fct_relevel(type, "pretest", "posttest"))

cor_df <- pl_int %>%
  tidyr::pivot_wider(names_from = type,
                     values_from = mean_pwc) %>%
  dplyr::mutate(improvement = posttest - pretest) %>%
  dplyr::select(id, speaker, ends_with("_c"), best_win, pretest, posttest, improvement)

@@

int_table <- pl_int %>%
  dplyr::filter(type == "pretest") %>%
  dplyr::select(id, speaker, age, ends_with("_c"), best_win) %>%
  dplyr::select(-fluid_cog_c) %>%
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Picture Sequence Memory` = pic_seq_c,
    `Words in Noise Threshold` = best_win
  ) %>%
  group_by(id, speaker) %>% 
  summarize(across(everything(), first)) %>% 
  ungroup() %>% 
  select(-id) %>% 
  tbl_summary(
    by = "speaker",
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing = "no",
    digits = list(everything() ~ c(2))
  ) %>% 
  add_p() %>%
  as_gt()

int_table

int_table %>%
  gt::gtsave("Tables/means_tabel.html")

@@

speaker_intel <- pl_int %>%
  dplyr::mutate(type = as.factor(type),
                type = fct_relevel(type, "pretest", "posttest")) %>%
  dplyr::group_by(speaker, type) %>%
  dplyr::summarize(pwc = mean(mean_pwc),
                   sd = sd(mean_pwc)) %>%
  dplyr::ungroup() %>%
  tidyr::pivot_wider(names_from = speaker,
                     values_from = c(pwc:sd)) %>%
  dplyr::relocate(sd_AM1, .after = pwc_AM1) %>%
  gt::gt() %>%
    fmt_number(columns = "pwc_AM1":"sd_PDM10", decimals = 2) %>%
    tab_spanner(label = "AM1",
                columns = c(pwc_AM1, sd_AM1)) %>%
    tab_spanner(label = "PDM10",
                columns = c(pwc_PDM10, sd_PDM10)) %>%
    cols_label(type = " ",
               pwc_AM1 = "Mean",
               sd_AM1 = "SD",
               pwc_PDM10 = "Mean",
               sd_PDM10 = "SD")

@@

pl_int %>%
  ggplot() +
  aes(x = type,
      y = mean_pwc,
      group = id) +
  geom_line(alpha = 0.3) +
  stat_summary(aes(group = speaker),
               fun.y = mean, geom = "line", linewidth = 2) +
  facet_wrap("speaker") +
  labs(x = "Phase", y = "Intelligibility") +
  theme_bw() +
  theme(legend.position = "none", aspect.ratio = 1)

@@

>>>>

# Calculating pretest and posttest intelligibility for the listeners
pl_int <- data %>%
  dplyr::group_by(id, speaker, type) %>%
  dplyr::mutate(pwc = (sum(correct_words)/sum(target_number))*100,
                best_win = ifelse(win_r < win_l, win_r, win_l)) %>%
  dplyr::summarize(pwc = mean(pwc, na.rm = T),
                   across(c(contains("_c"), contains("_u"), contains("win")),
                          ~first(.x)
                          )) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(type = as.factor(type),
                type = fct_relevel(type, "pretest", "posttest"))

@@

cor_df <- pl_int %>%
  tidyr::pivot_wider(names_from = type,
                     values_from = pwc) %>%
  dplyr::mutate(improvement = posttest - pretest) %>%
  dplyr::select(id, speaker, ends_with("_c"), best_win, pretest, posttest, improvement)

@@

cog_table <- pl_int %>%
  dplyr::filter(type == "pretest") %>%
  dplyr::select(id, speaker, age, ends_with("_c"), best_win) %>%
  dplyr::select(-fluid_cog_c) %>%
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Picture Sequence Memory` = pic_seq_c,
    `Words in Noise Threshold` = best_win
  ) %>%
  group_by(id, speaker) %>% 
  summarize(across(everything(), first)) %>% 
  ungroup() %>% 
  select(-id) %>% 
  tbl_summary(
    by = "speaker",
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing = "no",
    digits = list(everything() ~ c(2))
  ) %>% 
  add_p() %>%
  as_gt()

cog_table

cog_table %>%
  gt::gtsave("Tables/means_tabel.html")

@@

speaker_intel <- pl_int %>%
  dplyr::mutate(type = as.factor(type),
                type = fct_relevel(type, "pretest", "posttest")) %>%
  dplyr::group_by(speaker, type) %>%
  dplyr::summarize(m_pwc = mean(pwc),
                   sd_pwc = sd(pwc)) %>%
  dplyr::ungroup() %>%
  tidyr::pivot_wider(names_from = speaker,
                     values_from = c(m_pwc:sd_pwc)) %>%
  dplyr::relocate(sd_pwc_AM1, .after = m_pwc_AM1) %>%
  gt::gt() %>%
    fmt_number(columns = "m_pwc_AM1":"sd_pwc_PDM10", decimals = 2) %>%
    tab_spanner(label = "AM1",
                columns = c(m_pwc_AM1, sd_pwc_AM1)) %>%
    tab_spanner(label = "PDM10",
                columns = c(m_pwc_PDM10, sd_pwc_PDM10)) %>%
    cols_label(type = " ",
               m_pwc_AM1 = "Mean",
               sd_pwc_AM1 = "SD",
               m_pwc_PDM10 = "Mean",
               sd_pwc_PDM10 = "SD")

@@

pl_int %>%
  ggplot() +
  aes(x = type,
      y = pwc,
      group = id) +
  geom_line(alpha = 0.3) +
  stat_summary(aes(group = speaker),
               fun.y = mean, geom = "line", linewidth = 2) +
  facet_wrap("speaker") +
  labs(x = "Phase", y = "Intelligibility") +
  theme_bw() +
  theme(legend.position = "none", aspect.ratio = 1)

@@

rm(AM1_cor, PDM10_cor, cog_table, speaker_intel)
